---
title: "Untitled"
output: github_document
---

```{r settings, include=FALSE}
library(ggplot2)
library(knitr)
library(xtable)
library(DT)
library(readxl)
#opts_chunk$set()
opts_template$set(smallFig = list(fig.height=6, fig.width = 7))

knit_hooks$set(koreanG = function(before){
  if(before){
    library(extrafont)
    par(family="NanumGothic")
  }
},
koreanM = function(before){
  if(before){
    library(extrafont)
    par(family = "NanumMyeongjo")
  }
}
)
```

### 표 그리기 연습

```{r opts.label = 'smallFig', results='asis', echo=FALSE}
graduate_2018 <- read_excel("graduate_2018.xls")
graduate_2018$단과대학 = as.factor(graduate_2018$단과대학)
graduate_2018$학과명 = as.factor(graduate_2018$학과명)
graduate_2018$백분율점수구간 = as.factor(graduate_2018$백분율점수구간)

## double click the cell to edit..!
datatable(graduate_2018, editable = TRUE,filter = 'top', options = list(
  pageLength = 9, autoWidth = TRUE, initComplete = JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'font-size': '10px'});",
    "}")
)) %>%
formatStyle(1:8, `font-size` = '9pt')
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
